\documentclass[11pt,letterpaper]{article}

%% ─── Packages ───────────────────────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows.meta,shapes.geometric}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tcolorbox}
\tcbuselibrary{skins,breakable}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mdframed}

%% ─── Geometry ───────────────────────────────────────────────────────────────
\geometry{
  letterpaper,
  top=1.0in, bottom=1.0in,
  left=1.15in, right=1.15in,
  headheight=14pt,
  headsep=18pt
}

%% ─── Color palette ──────────────────────────────────────────────────────────
\definecolor{SCblue}{RGB}{10,50,110}
\definecolor{SCaccent}{RGB}{0,110,170}
\definecolor{SCgold}{RGB}{170,120,0}
\definecolor{SCgray}{RGB}{75,85,95}
\definecolor{SClight}{RGB}{234,240,248}
\definecolor{SCgreen}{RGB}{15,95,55}
\definecolor{SCredrule}{RGB}{140,30,30}

%% ─── Hyperref ───────────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  linkcolor=SCaccent,
  urlcolor=SCaccent,
  citecolor=SCgray,
  pdftitle={DSFB Structural Semiotics Engine for Semiconductor Process Control},
  pdfauthor={Riaan de Beer},
  pdfkeywords={semiconductor process control, fault detection, structural semiotics,
    DSFB, SECOM, admissibility envelope, deterministic diagnostics,
    augmentation layer, SPC, APC, run-to-run control}
}

%% ─── Typography ─────────────────────────────────────────────────────────────
\setstretch{1.09}

%% ─── Section formatting ─────────────────────────────────────────────────────
\titleformat{\section}
  {\color{SCblue}\large\bfseries}
  {\thesection.}{0.6em}{}
  [\vspace{-4pt}\color{SCblue}\rule{\linewidth}{0.7pt}\vspace{2pt}]

\titleformat{\subsection}
  {\color{SCgray}\normalsize\bfseries}
  {\thesubsection}{0.5em}{}

\titleformat{\subsubsection}
  {\color{SCaccent}\normalsize\itshape}
  {}{0em}{}

\titlespacing{\section}{0pt}{14pt}{6pt}
\titlespacing{\subsection}{0pt}{10pt}{4pt}

%% ─── Header / Footer ────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\footnotesize\color{SCgray}\textit{DSFB Structural Semiotics Engine
  for Semiconductor Process Control}}
\fancyhead[R]{\footnotesize\color{SCgray}Invariant Forge LLC}
\fancyfoot[C]{\footnotesize\color{SCgray}\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{\hbox to\headwidth{%
  \color{SCaccent}\leaders\hrule height \headrulewidth\hfill}}

%% ─── Theorem environments ───────────────────────────────────────────────────
\newtheoremstyle{scresult}
  {8pt}{6pt}{\itshape}{0pt}{\color{SCblue}\bfseries}{.}{0.5em}{}
\theoremstyle{scresult}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

%% ─── Box environments ───────────────────────────────────────────────────────
\tcbset{
  lawbox/.style={
    enhanced, breakable,
    colback=white, colframe=SCblue,
    boxrule=1pt, arc=2pt,
    left=10pt, right=10pt, top=8pt, bottom=8pt,
    coltitle=black, colbacktitle=white,
    fonttitle=\bfseries,
    toptitle=2mm, bottomtitle=2mm
  },
  claimbox/.style={
    enhanced,
    colback=SClight, colframe=SCaccent,
    boxrule=0.8pt, arc=2pt,
    left=8pt, right=8pt, top=5pt, bottom=5pt
  },
  augbox/.style={
    enhanced,
    colback=white, colframe=SCgreen,
    boxrule=1pt, arc=2pt,
    left=8pt, right=8pt, top=5pt, bottom=5pt,
    borderline west={3pt}{0pt}{SCgreen}
  },
  warnbox/.style={
    enhanced,
    colback=white, colframe=SCgold,
    boxrule=0.8pt, arc=2pt,
    left=8pt, right=8pt, top=5pt, bottom=5pt,
    borderline west={3pt}{0pt}{SCgold}
  }
}

%% ─── List styling ────────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.4em, itemsep=2pt, parsep=0pt, topsep=4pt,
  label={\color{SCaccent}\small$\blacktriangleright$}
}
\setlist[enumerate]{
  leftmargin=1.6em, itemsep=2pt, parsep=0pt, topsep=4pt
}

%% ─── Math macros ─────────────────────────────────────────────────────────────
\newcommand{\R}{\mathbb{R}}
\newcommand{\norm}[1]{\left\|#1\right\|}
\newcommand{\Engine}{\mathcal{M}}
\newcommand{\envelope}{\mathcal{E}}
\newcommand{\bank}{\mathcal{H}}

%% ─── Caption styling ─────────────────────────────────────────────────────────
\captionsetup{
  font={small,color=SCgray},
  labelfont={bf,color=SCblue},
  skip=4pt
}

%% ═══════════════════════════════════════════════════════════════════════════
\begin{document}
%% ═══════════════════════════════════════════════════════════════════════════

%% ─── Title ───────────────────────────────────────────────────────────────────
\begin{center}
{\color{SCblue}\rule{\linewidth}{1.5pt}}
\vspace{8pt}

{\LARGE\bfseries\color{SCblue}
DSFB Structural Semiotics Engine\\[6pt]
for Semiconductor Process Control}

\vspace{6pt}
{\large\itshape\color{SCaccent}
A Deterministic Augmentation Layer for Typed Residual Interpretation\\
for Fault Detection and Run-to-Run Variation\\
in Advanced Manufacturing}

\vspace{8pt}
{\color{SCblue}\rule{\linewidth}{0.8pt}}

\vspace{12pt}

{\normalsize
Riaan de Beer\\
\texttt{riaan@invariantforge.net}\\
Chief Research Advisor, Invariant Forge LLC\\
ORCID: 0009-0006-1155-027X\\[4pt]
DOI: \textit{pending}\\
\texttt{https://github.com/infinityabundance/dsfb}\\[4pt]
Version 1.0 \quad March 2026
}

\vspace{12pt}

\begin{minipage}{0.88\linewidth}
\begin{center}
\textbf{Abstract}
\end{center}
\small
Semiconductor process monitoring already produces dense residual streams through
statistical process control (SPC), run-to-run and advanced process control
(APC), and fault detection and classification (FDC) systems, but operational
action is still dominated by scalar alarms that suppress temporal structure.
This paper studies the DSFB Structural Semiotics Engine as a deterministic
augmentation layer over those existing residual streams. It does not propose a
replacement controller or a new fab-wide monitoring stack. Instead, it maps
residual trajectories into explicit objects --- residual sign, admissibility
envelope, grammar state, and provenance-aware motif entries --- so that slow
drift, boundary approach, and structural excursion can be represented in a
typed and inspectable form.

The paper makes a bounded claim. It shows how deterministic intermediate
representations can support auditability arguments and operator review, and how
the DSFB formal objects can be instantiated using semiconductor observables such
as innovation residuals, control limits, and specification windows. It does not
prove SEMI standards compliance, completed qualification, universal superiority
over SPC/EWMA/FDC/ML baselines, or physical chamber-mechanism attribution from
public benchmark data.

The empirical evidence is Stage~II public-benchmark evidence on the SECOM
dataset. SECOM is used here as a recognized but anonymized semiconductor
manufacturing benchmark for real-data evaluation of residual structure and
failure-preceding motifs. The study fixes a healthy-window nominal reference, a
$3\sigma$ admissibility envelope, a drift window, and a weak $3\sigma$
magnitude comparator. Within that bounded setting, the main result is
interpretive feasibility rather than definitive performance superiority: the
DSFB layer yields typed structural descriptions of residual evolution on real
semiconductor data, while the scalar baseline remains magnitude-only. This
positions the method for later qualification work and for stronger benchmark
stages on richer run-to-failure semiconductor datasets.
\end{minipage}

\vspace{8pt}
{\color{SCblue}\rule{\linewidth}{0.8pt}}
\end{center}

\vspace{6pt}
{\footnotesize\color{SCgray}
\textbf{IP Notice.}
The theoretical framework, formal constructions, and supervisory methods described
herein constitute proprietary Background IP of Invariant Forge LLC
(Delaware LLC No.\ 10529072), with prior art established by this publication and
earlier Zenodo DOI publications by the same author. Commercial deployment requires
a separate written license. Reference implementations are released under
Apache~2.0. Licensing: \texttt{licensing@invariantforge.net}
}

\clearpage
\tableofcontents
\clearpage

%% ═══════════════════════════════════════════════════════════════════════════
\section{Introduction}
\label{sec:intro}
%% ═══════════════════════════════════════════════════════════════════════════

\subsection{Motivation}

Semiconductor fabrication is among the most instrumented industrial processes
in existence. A modern 300mm fab produces millions of sensor measurements per
wafer run, spanning plasma power, gas flow rates, chamber pressure, optical
emission spectra, etch depth, deposition uniformity, and dozens of electrical
test parameters. Despite this instrumentation density, a central challenge
persists: distinguishing \emph{structured degradation} from \emph{normal
process variation} early enough to intervene before yield loss.

The dominant paradigm for residual-based process monitoring in semiconductor
manufacturing is statistical. Statistical Process Control (SPC) compares
measurements against control limits derived from historical variance. EWMA
controllers smooth innovation sequences into scalar signals that drive
run-to-run adjustments. Fault Detection and Classification (FDC) systems alarm
when multivariate sensor profiles deviate from empirical baselines. Probabilistic
fault detectors apply likelihood ratio tests or principal component analysis
to identify out-of-control conditions.

These methods share a structural limitation. They treat residuals primarily as
magnitudes to be compared against thresholds. A residual that grows slowly,
persistently, and directionally --- the signature of tool aging, chamber
seasoning drift, consumable degradation, or recipe creep --- may remain below
alarm thresholds for many wafer runs while its structural organization already
encodes the onset of a systematic process shift. By the time the shift becomes
statistically significant, the drift has been underway for hours or days.

\subsection{The Structural Opportunity}

The DSFB Structural Semiotics Engine addresses this limitation by treating
residual trajectories as primary inferential objects rather than sequences of
scalar discrepancies. The key insight is not new in spirit --- process engineers
already read drift patterns informally from SPC charts --- but it has not
previously been formalized into a deterministic and reusable
interpretive architecture.

The core claim of this paper is precise:

\begin{tcolorbox}[claimbox]
The innovation residuals produced by EWMA controllers, SPC systems, and
probabilistic fault detectors contain structured temporal information --- drift
direction, curvature of change, and admissibility relative to process
constraints --- that scalar alarm methods discard. The DSFB Structural Semiotics
Engine recovers and formalizes this structure as a typed, composable,
reusable interpretive layer.
\end{tcolorbox}

This is an augmentation claim, not a replacement claim. The engine does not
ask fabs to remove their SPC infrastructure, retrain their FDC models, or
replace their APC controllers. It reads the residuals those systems already
produce and provides a parallel structural interpretation alongside them.

\subsection{Operational Objects and Decision Boundary}

The formal objects required for this paper are intentionally limited. The
residual $r(k)$ denotes the run-indexed deviation between a measured sensor or
derived process variable and its nominal reference. The admissibility envelope
$\mathcal{E}(k)$ defines the region considered operationally acceptable under
the chosen process limits or healthy-window statistics. The grammar layer maps
the residual trajectory to interpretable states such as \texttt{Admissible},
\texttt{Boundary}, and \texttt{Violation}. The heuristics bank records named
motifs together with provenance tags describing where those motifs came from.

These objects justify bounded decisions: continue monitoring, request
maintenance review, escalate an out-of-control event, or register a motif for
future interpretation. They do \emph{not} by themselves justify physical
root-cause attribution, autonomous recipe modification, cross-tool transfer
without recalibration, or standards-compliance claims.

\subsection{Relation to the DSFB Framework}

This paper is a domain application of the DSFB Structural Semiotics Engine
for General Systems~\cite{dsfb-semiotics-general}, which establishes the
foundational theory, formal results, and reference implementation. The full
theoretical treatment --- including all definitions, theorems, proofs, and
the Kani-verified bounded arithmetic invariants --- is contained in that
paper. The present paper is written to stand on its own for the semiconductor
reader: it restates only the formal objects and interpretations needed for
process control, then evaluates the bounded claim on the SECOM public dataset.

\subsection{Scope, Assumptions, and Non-Claims}

The framework is deterministic in construction but does not claim that
semiconductor processes are noise-free or fully deterministic in ontology.
The claim is methodological: a deterministic interpretive layer can be built
over process residual trajectories even in settings where measurement noise,
lot-to-lot variation, and model imperfection remain present.

This paper does not claim:
\begin{itemize}
  \item that the semiotic approach subsumes SPC, EWMA, FDC, or probabilistic
        fault detection in all process regimes;
  \item that the SECOM demonstration constitutes a complete empirical
        validation of the framework for all semiconductor process classes;
  \item that the current SECOM evidence supports chamber-mechanism attribution
        or physical root-cause identification;
  \item that admissibility envelopes derived from process specification windows
        are universally optimal or automatically calibrated;
  \item that the present manuscript establishes SEMI~E10 or E116 compliance,
        completed qualification, or deployment readiness;
  \item or that the heuristics bank, in its current form, exhausts the
        interpretive possibilities of real fab environments.
\end{itemize}

These limitations are addressed explicitly in Section~\ref{sec:limitations}.

\subsection{Contributions of This Paper}

\begin{enumerate}
  \item \textbf{Process control instantiation.} Formal mapping of DSFB
        objects --- residual signs, drift, slew, admissibility envelopes,
        grammar, and heuristics bank --- onto semiconductor process control
        constructs: innovation sequences, control limits, spec windows,
        operator review states, and residual motifs.

  \item \textbf{Augmentation architecture.} A formal characterization of
        how the structural semiotics engine sits on top of existing APC
        infrastructure without modifying it, and what the combination
        provides that neither component alone delivers.

  \item \textbf{Formal results in process context.} Direct interpretation
        of Law~1 (Structural Detectability Principle), Theorem~1
        (finite-time envelope exit), Theorem~9 (deterministic
        interpretability), and Theorem~10 (auditable early-warning
        inference) in the semiconductor process control setting.

  \item \textbf{SECOM Stage~II demonstration.} Application of the engine
        to the SECOM public dataset with explicit nominal model, envelope
        parameterization, weak-baseline discipline, and typed motif outputs
        on real semiconductor data.

  \item \textbf{Qualification relevance.} A bounded argument for why
        deterministic and reproducible intermediate representations are
        relevant to later qualification workflows, without claiming that
        qualification is already complete.
\end{enumerate}

\subsection{Paper Map}

Section~\ref{sec:background} reviews semiconductor process control and its
residual monitoring infrastructure. Section~\ref{sec:instantiation} formally
instantiates DSFB objects in the process control setting.
Section~\ref{sec:formal} interprets the key formal results in this domain.
Section~\ref{sec:augmentation} develops the augmentation architecture.
Section~\ref{sec:incumbent} compares the framework against incumbent methods.
Section~\ref{sec:demonstration} presents the SECOM Stage~II demonstration.
Section~\ref{sec:certification} discusses qualification relevance and the
integration pathway. Section~\ref{sec:limitations} states limitations.
Section~\ref{sec:conclusion} concludes.

%% ═══════════════════════════════════════════════════════════════════════════
\section{Background: Semiconductor Process Control and Residual Monitoring}
\label{sec:background}
%% ═══════════════════════════════════════════════════════════════════════════

\subsection{The Run-to-Run Control Architecture}

Semiconductor fabrication consists of hundreds of tightly interdependent
processing steps applied sequentially to each wafer. Process control operates
at multiple timescales: within-run (real-time sensor monitoring during a single
process step), run-to-run (adjustment of recipe parameters between consecutive
wafer runs based on measured outcomes), and lot-to-lot (longer-horizon
adjustments across wafer batches).

Run-to-run (R2R) control is the primary locus of residual-based monitoring in
advanced process control. The R2R controller maintains a process model
$\hat{y}(k)$ predicting the output of run $k$ given the current recipe and tool
state. After each run, the measured output $y(k)$ is compared to the prediction,
producing an innovation residual:
\begin{equation}
  r(k) = y(k) - \hat{y}(k).
  \label{eq:r2r-residual}
\end{equation}
The controller uses $r(k)$ to update the recipe for run $k+1$. In EWMA-based
R2R control, the smoothed residual drives the adjustment:
\begin{equation}
  \hat{d}(k) = \lambda r(k) + (1 - \lambda)\hat{d}(k-1),
  \label{eq:ewma}
\end{equation}
where $\hat{d}(k)$ is the estimated process disturbance and $\lambda \in (0,1]$
is the EWMA weight. The controller suppresses $\hat{d}(k)$ by adjusting the
recipe, thereby driving future residuals toward zero.

\subsection{Fault Detection and Classification in APC}

Fault Detection and Classification (FDC) systems monitor inline sensor streams
during process steps to detect equipment malfunctions, recipe deviations, and
process excursions. In advanced fabs, FDC systems collect hundreds to thousands
of sensor channels per process step, including:
\begin{itemize}
  \item plasma power, voltage, and reflected power in etch and deposition steps;
  \item gas flow rates and chamber pressure;
  \item optical emission spectroscopy (OES) signatures;
  \item endpoint detection signals;
  \item and temperature profiles across the wafer chuck and chamber walls.
\end{itemize}

Traditional FDC compares each sensor channel against univariate control limits
derived from historical data. Multivariate FDC applies principal component
analysis (PCA) or partial least squares (PLS) to detect correlated
multi-sensor deviations. Both approaches produce scalar alarm signals: either
a specific sensor has exceeded its limit, or the multivariate score has exceeded
a threshold.

\subsection{Statistical Process Control and Its Structural Limits}

SPC in semiconductor manufacturing applies Shewhart control charts, CUSUM
statistics, and EWMA charts to post-process measurement data: etch rate,
critical dimension (CD), film thickness, overlay error, particle counts, and
electrical test yields. Control limits are set at $\pm 3\sigma$ of the
historical distribution under normal process conditions.

The structural limitation of SPC is well-recognized in the literature. Control
limits are calibrated to the historical noise distribution, which means:
\begin{itemize}
  \item slow, persistent drift remains within $3\sigma$ bounds for many
        consecutive runs before triggering an alarm;
  \item the magnitude of a residual at any single run provides no information
        about its temporal direction or structural organization;
  \item regime transitions --- such as the onset of chamber seasoning or
        consumable wear --- appear as gradual shifts that SPC interprets as
        noise until the shift exceeds the control limit.
\end{itemize}

This is precisely the regime where the DSFB structural semiotics engine adds
value: it reads the temporal organization of residuals that SPC is tracking,
identifies directional drift before the control limit is reached, and produces
a typed structural interpretation of what the drift pattern means.

\subsection{The EWMA Residual as a Semiotic Object}

The EWMA innovation sequence $\{r(k)\}$ is already the right object for
structural interpretation. It is:
\begin{itemize}
  \item centered at zero under nominal process conditions, making deviations
        directly interpretable as structured departures from the nominal
        prediction;
  \item temporally indexed, preserving the run-order information that scalar
        FDC discards;
  \item and already computed by the existing APC infrastructure, requiring
        no additional instrumentation.
\end{itemize}

The structural semiotics engine reads $\{r(k)\}$ and computes, at each step:
the sign tuple $(\norm{r(k)}, \dot{r}(k), \ddot{r}(k))$, the grammar state
relative to the admissibility envelope, and the semantic disposition relative
to the heuristics bank. This computation is a pure function of the residual
history --- it modifies nothing in the existing controller.

\subsection{Where Existing Methods Fail: The Slow Drift Problem}

The canonical failure mode that motivates this work is slow tool degradation.
Consider a plasma etch chamber whose etch rate drifts downward by 0.5\% per
hundred wafer runs due to chamber wall coating buildup. Over 500 runs, the
cumulative drift is 2.5\% --- well within typical $3\sigma$ bounds for etch
rate variation. The FDC system detects nothing. The R2R controller compensates
by adjusting the recipe, masking the drift from the output residual. But the
compensation itself is a structured signal: the recipe adjustments are growing,
and the innovation residuals are exhibiting persistent directional organization.

The DSFB structural semiotics engine reads this organization. The drift
component $\dot{r}(k)$ is persistently positive (or negative, depending on
sign convention). The admissibility grammar detects sustained outward evolution.
Theorem~1 provides a finite-time detectability bound: if drift exceeds $\alpha$
per run, the residual must exit the admissibility envelope within
$t^* \leq \rho/\alpha$ runs. The engine fires an early-warning signal while
the SPC chart still shows green.

%% ═══════════════════════════════════════════════════════════════════════════
\section{DSFB Framework Instantiated in Process Control}
\label{sec:instantiation}
%% ═══════════════════════════════════════════════════════════════════════════

\subsection{System Setting}

We consider a semiconductor process tool operating over a sequence of wafer
runs $k = 0, 1, \ldots, K$. The system state $x(k) \in \R^n$ represents the
relevant process outputs and sensor measurements at run $k$. The nominal
prediction $\hat{x}(k) \in \R^n$ is produced by the process model --- which
may be a physics-based model, a data-driven model, or the EWMA-smoothed
historical mean. The residual is:
\begin{equation}
  r(k) = x(k) - \hat{x}(k) \in \R^n.
\end{equation}
No assumption is made that the model is exact or that $r(k)$ is noise-free.
The residual is treated as a time-indexed trajectory rather than a sequence
of independent scalar discrepancies.

\subsection{Residual Sign in Process Control}

Following the general framework, the \emph{residual sign} at run $k$ is the
tuple:
\begin{equation}
  \sigma(k) = \bigl(\norm{r(k)},\; \dot{r}(k),\; \ddot{r}(k)\bigr),
\end{equation}
where $\dot{r}(k)$ is the finite-difference drift (run-to-run rate of change
of the residual norm) and $\ddot{r}(k)$ is the slew (second difference,
capturing curvature of the residual trajectory).

In process control terms:
\begin{itemize}
  \item $\norm{r(k)}$ is the instantaneous process deviation --- what SPC
        monitors;
  \item $\dot{r}(k)$ is the drift rate --- the directional evolution that
        SPC ignores;
  \item $\ddot{r}(k)$ is the slew --- the acceleration of deviation, which
        signals abrupt regime changes such as consumable failure or recipe
        excursion.
\end{itemize}

\subsection{Admissibility Envelopes from Process Specification}

The admissibility envelope $\mathcal{E}(k)$ defines structurally acceptable
residual behavior at run $k$. In semiconductor process control, natural sources
for envelope construction include:

\begin{itemize}
  \item \textbf{Process specification windows:} the $\pm$tolerance on critical
        dimensions, etch rates, and film thicknesses defines the outer
        admissibility bound.
  \item \textbf{SPC control limits:} the $3\sigma$ bound on the historical
        residual distribution under normal conditions defines a conservative
        inner envelope.
  \item \textbf{R2R controller authority:} the maximum recipe adjustment
        allowed by the controller provides an implicit drift admissibility
        constraint.
  \item \textbf{Engineering release limits:} chamber qualification windows and
        locally approved engineering limits can provide additional envelope
        constraints when such limits exist for the specific tool and recipe.
\end{itemize}

The envelope is constructed as:
\begin{equation}
  \mathcal{E}(k) = \{r \in \R^n : \norm{r} \leq \rho(k)\},
\end{equation}
where $\rho(k)$ is the regime-dependent envelope radius, derived from the
above sources. In practice, $\rho$ is set from the $3\sigma$ healthy residual
distribution estimated over an initial qualification window.

\subsection{Grammar Layer: Process Fault States}

The grammar evaluation maps each run's semiotic trajectory to one of three
states:
\begin{itemize}
  \item \textbf{Admissible:} the residual is within the envelope and its
        drift is inward-compatible or bounded. Process is operating nominally.
  \item \textbf{Boundary:} the residual is approaching the envelope boundary
        with sustained outward drift. Early-warning state.
  \item \textbf{Violation:} the residual has exited the envelope. Structural
        fault state, corresponding to an actionable process excursion.
\end{itemize}

Grammar reason codes in the process control context:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}p{4.5cm}p{7cm}@{}}
\toprule
\textbf{Reason Code} & \textbf{Process Control Interpretation} \\
\midrule
\texttt{SustainedOutwardDrift} & Tool degradation, chamber seasoning,
  consumable wear \\
\texttt{AbruptSlewViolation} & Recipe excursion, hardware fault, gas
  delivery failure \\
\texttt{RecurrentBoundaryGrazing} & Cyclic process variation, periodic
  maintenance effects \\
\texttt{EnvelopeViolation} & Confirmed process out-of-control condition \\
\texttt{Admissible} & Normal process operation \\
\texttt{Boundary} & Approaching control limit, monitoring recommended \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Semantic Layer: Heuristics Bank for Process Faults}

The heuristics bank $\mathcal{H}$ is a typed, provenance-aware library of
recurrent residual motifs accumulated from process experience. In the
semiconductor context, canonical heuristics bank entries include:

\begin{itemize}
  \item \textbf{Slow etch rate drift:} persistent positive $\dot{r}$ in etch
        rate residual over 100--500 runs; associated with chamber wall buildup;
        predictive of CD deviation if uncorrected.
  \item \textbf{Deposition rate step change:} abrupt slew spike followed by
        new steady-state offset; associated with target change or cathode
        replacement.
  \item \textbf{Gas flow oscillation:} bounded oscillatory residual in flow
        rate channel; associated with MFC degradation or pressure regulator
        instability.
  \item \textbf{Seasoning drift:} slow negative drift in OES endpoint
        signal over first 50--100 runs after chamber clean; self-correcting
        under normal conditions, requiring wider envelope during seasoning
        window.
  \item \textbf{R2R over-compensation signature:} alternating-sign residual
        with growing amplitude; indicates EWMA weight mismatch with current
        process gain.
\end{itemize}

Each entry carries: a motif descriptor, the applicable process regime and tool
class, the associated physical mechanism hypothesis, and provenance (whether
derived from framework design, historical data, simulation, or field
deployment). In this paper these entries should be read as framework-level
examples rather than as validated chamber-mechanism attributions from the
SECOM study.

\subsection{Endoductive Inference in Process Control}

The general framework introduces \emph{endoduction} as the inference mode in
which candidate interpretations emerge from the organized structure of residual
trajectories without requiring a pre-specified fault hypothesis class. In the
semiconductor context, this is operationally significant:

A new process node or tool generation introduces fault modes that are not yet
in the heuristics bank. A purely abductive system (GLR, FDC) may fail to name
or prioritize such faults when their hypothesis class does not include them. The
endoductive engine detects the structural organization of the residual ---
the drift, the slew, the admissibility grammar state --- and returns
\texttt{Unknown} semantic disposition with a fully characterized semiotic
trajectory. This is actionable: the process engineer sees a structured
description of what the residual is doing, even before a named fault
interpretation is available. The motif can then be registered in the heuristics
bank as a new entry, making the system progressively more capable with each
deployment.

%% ═══════════════════════════════════════════════════════════════════════════
\section{Key Formal Results in the Process Control Setting}
\label{sec:formal}
%% ═══════════════════════════════════════════════════════════════════════════

\subsection{Law 1: Structural Detectability Principle}

\begin{tcolorbox}[lawbox,
  title={\textsc{Law 1} \quad Structural Detectability Principle}]
Detectability is governed by the structural separation of residual trajectories
relative to regime-dependent admissibility envelopes, rather than by residual
magnitude alone. A trajectory that remains small but drifts persistently outward
is more detectable --- and more interpretively significant --- than one that
oscillates at larger amplitude within admissible bounds.

\medskip
\textit{Process control corollary.} A tool whose etch rate is drifting
persistently but slowly is more structurally detectable --- and more actionable
--- than one exhibiting large but bounded run-to-run variation. Scalar control
limits primarily emphasize the second. The structural semiotics engine is
designed to distinguish both cases explicitly.
\end{tcolorbox}

\subsection{Theorem 1: Finite-Time Envelope Exit in Process Context}

Theorem~1 of the general framework states: if the residual norm grows at rate
$\geq \alpha > 0$ starting inside an envelope of radius $\rho$, then exit
occurs within $t^* \leq \rho/\alpha$ steps.

In semiconductor process control, this result bounds the number of wafer runs
before a drifting tool will trigger a structural alarm:

\begin{tcolorbox}[claimbox]
\textbf{Process interpretation.} Let $\rho$ be the $3\sigma$ residual bound
estimated from the qualification window, and let $\alpha$ be the observed
drift rate in residual units per run. Then the number of runs before structural
detection is:
\[
  k^* \leq \frac{\rho}{\alpha}.
\]
\end{tcolorbox}

This is not a guarantee of earlier detection than SPC in all cases; it is a
structural upper bound on the detection window under sustained drift. The
bound is computable from observable quantities and requires no noise model.

\subsection{Theorem 9: Deterministic Interpretability and APC Auditability}

Theorem~9 of the general framework establishes that the engine is a
deterministic function from system trajectory to interpretation: identical
residual sequences always produce identical semiotic outputs under fixed
admissibility conditions and a fixed heuristics bank.

In semiconductor manufacturing, this property is relevant to qualification
workflows because reproducible monitoring behavior is easier to document,
review, and troubleshoot than behavior that depends on stochastic sampling,
model initialization, or runtime randomness. The structural semiotics engine
provides that determinism at the interpretive-layer level under fixed inputs,
fixed envelope construction, and a fixed heuristics bank.

\subsection{Theorem 10: Auditable Early-Warning Inference}

Theorem~10 establishes the conjunction of determinism, finite-time
detectability, and auditability through explicit intermediate representations.
In the APC context:

\begin{itemize}
  \item \textbf{Early warning:} under sustained drift, structural deviation may
        become visible before a scalar threshold alarm fires. This is a lead-time
        mechanism, not a universal superiority claim over SPC or FDC.
  \item \textbf{Determinism:} the detection and interpretation are reproducible
        under fixed inputs and parameters, which is relevant to later
        qualification workflows.
  \item \textbf{Auditability:} the intermediate representations --- residual
        norm, drift, slew, grammar state, semantic disposition --- provide a
        traceable inference path that process engineers and equipment suppliers
        can inspect directly.
\end{itemize}

%% ═══════════════════════════════════════════════════════════════════════════
\section{The Augmentation Architecture}
\label{sec:augmentation}
%% ═══════════════════════════════════════════════════════════════════════════

\subsection{Positioning Statement}

\begin{tcolorbox}[augbox]
The DSFB Structural Semiotics Engine does not replace SPC, EWMA control, GLR
fault detection, or multivariate FDC. It is the interpretive layer that sits
on top of these systems, reading the residuals they already produce, and making
their structural meaning explicit, typed, and reusable. The combination delivers
what neither component alone provides: calibrated false-alarm rates from
the probabilistic layer, and structured early-warning interpretation from
the deterministic layer.
\end{tcolorbox}

\subsection{The Residual Handoff}

The augmentation architecture operates through a clean residual handoff. The
existing APC infrastructure produces an innovation sequence $\{r(k)\}$ as a
byproduct of its normal operation. The structural semiotics engine receives
this sequence and computes its semiotic interpretation in parallel, without
modifying the controller, the FDC system, or the SPC chart.

\begin{center}
\begin{tikzpicture}[
  node distance=0.6cm,
  box/.style={rectangle, rounded corners=3pt, draw=SCblue, fill=SClight,
    minimum width=2.8cm, minimum height=0.7cm,
    font=\small\bfseries\color{SCblue}, align=center},
  sbox/.style={rectangle, rounded corners=3pt, draw=SCgreen, fill=white,
    minimum width=2.8cm, minimum height=0.7cm,
    font=\small\bfseries\color{SCgreen}, align=center},
  arr/.style={->,>=Stealth,thick,color=SCaccent},
  darr/.style={->,>=Stealth,thick,color=SCgreen,dashed}
]
\node[box] (tool) {Process Tool};
\node[box, right=0.5cm of tool] (apc) {APC / EWMA\\Controller};
\node[box, right=0.5cm of apc] (spc) {SPC / FDC\\Alarm};
\node[sbox, below=0.8cm of apc] (dsfb) {DSFB Semiotics\\Engine};
\node[sbox, right=0.5cm of dsfb] (interp) {Typed Structural\\Interpretation};

\draw[arr] (tool) -- node[above,font=\tiny]{$x(k)$} (apc);
\draw[arr] (apc) -- node[above,font=\tiny]{alarm} (spc);
\draw[darr] (apc) -- node[right,font=\tiny]{$r(k)$} (dsfb);
\draw[darr] (dsfb) -- node[above,font=\tiny]{$\sigma(k)$, grammar,} 
  node[below,font=\tiny]{semantics} (interp);
\end{tikzpicture}
\end{center}

\vspace{6pt}

The dashed green path is the augmentation layer. It is passive with respect
to the existing control loop: $r(k)$ is read but not modified. The controller
continues operating exactly as before.

\subsection{What the Combination Provides}

\begin{center}
\small
\renewcommand{\arraystretch}{1.35}
\begin{tabular}{@{}p{3.8cm}p{3.0cm}p{3.0cm}p{2.4cm}@{}}
\toprule
\textbf{Capability} & \textbf{SPC / EWMA alone} & \textbf{DSFB alone} &
  \textbf{Combined} \\
\midrule
Calibrated false-alarm rate & Yes (under model) & No & Yes \\
Structured indication under sustained drift & Limited & Yes & Yes \\
Typed residual interpretation & No & Yes & Yes \\
Provenance-aware motif accumulation & No & Yes & Yes \\
Qualification relevance & Statistical validation & Audit trail & Both \\
Structured unknown-state handling & Limited & Yes & Yes \\
Auditable inference path & Partial & Yes & Yes \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Joint Decision Logic}

In the combined architecture, the alarm decision can be formed from the
conjunction of the SPC signal and the DSFB grammar state:

\begin{itemize}
  \item \textbf{SPC alarm + DSFB Violation:} confirmed structural fault.
        High confidence. Escalate.
  \item \textbf{No SPC alarm + DSFB Boundary (SustainedOutwardDrift):}
        early-warning state. Initiate preventive maintenance evaluation.
        This is the regime where DSFB adds most value.
  \item \textbf{SPC alarm + DSFB Admissible:} likely transient excursion
        or noise spike. Investigate before escalating.
  \item \textbf{No SPC alarm + DSFB Admissible:} normal process operation.
\end{itemize}

This joint logic is intended to help separate transient scalar alarms from
sustained structural drift, but its effect on false escalations and response
quality remains an empirical question for later-stage industrial evaluation.

\subsection{The Heuristics Bank as Accumulated Operational Intelligence}

The heuristics bank provides the mechanism by which the augmentation layer
grows more capable over deployment lifetime. Each new fault event, once
resolved and understood, can be registered as a named heuristics bank entry
with its semiotic motif descriptor, applicable tool class, process regime,
and provenance. Future occurrences of the same motif are then recognized
and named --- not merely alarmed --- providing the process engineer with a
structural explanation rather than a bare threshold crossing.

This is the long-horizon value of the framework: not just possible early
warning, but the progressive accumulation of interpretive knowledge that can
make the surrounding monitoring stack more legible and more reusable across
related tool families and process nodes.

%% ═══════════════════════════════════════════════════════════════════════════
\section{Relation to Incumbent Methods}
\label{sec:incumbent}
%% ═══════════════════════════════════════════════════════════════════════════

\subsection{DSFB and SPC (Shewhart, CUSUM, EWMA)}

SPC methods alarm when a residual exceeds a statistically derived threshold.
They are calibrated to provide a specified false-alarm rate under the assumption
that the residual process is stationary and normally distributed. Their
detection power for step changes is well-characterized; their detection power
for slow monotone drift depends on the CUSUM or EWMA accumulation parameter.

The structural semiotics engine is not calibrated to false-alarm rates. It
detects structural organization --- drift direction, admissibility grammar
state --- regardless of whether the instantaneous residual has crossed a
threshold. In regimes where drift is slow and persistent, it can provide
earlier structural indication. In regimes where the residual oscillates near a threshold, SPC
provides better calibrated alarm behavior.

The correct relationship is complementarity: SPC provides the statistical
guarantee; DSFB provides the structural interpretation.

\subsection{DSFB and Multivariate FDC (PCA, Hotelling $T^2$)}

Multivariate FDC applies dimensionality reduction (typically PCA) to
high-dimensional sensor vectors and detects deviations from the principal
component subspace. It is powerful for detecting sudden correlated
multi-sensor excursions.

Multivariate FDC discards temporal structure: each wafer run is treated as
an independent observation. The structural semiotics engine is the
temporal complement: it reads the run-order structure of residuals rather
than their cross-sensor covariance. The two approaches address different
aspects of the same fault detection problem.

\subsection{DSFB and Machine Learning FDC}

Machine learning FDC systems --- autoencoders, random forests, deep neural
networks, domain adaptation networks --- provide high classification accuracy
on labeled historical datasets. Their limitations in the process control
context are well-documented:
\begin{itemize}
  \item they require labeled fault data, which is scarce for new fault modes;
  \item their internal representations are not interpretable by process
        engineers or equipment suppliers;
  \item they do not provide finite-time detection guarantees;
  \item and their outputs may be harder to audit in qualification workflows.
\end{itemize}

The structural semiotics engine addresses some of these issues in a
complementary way. It operates without labeled fault data (endoductive
inference), produces typed interpretable outputs, provides computable detection
bounds under the stated assumptions, and generates an explicit intermediate
representation chain. It is not a competing classification system; it is an
interpretive layer that can make ML FDC outputs more structurally legible when
the deployment context justifies pairing them.

\subsection{Limitations Relative to Incumbent Methods}

The structural semiotics engine does not provide calibrated false-alarm rates
equivalent to those available from SPC under a valid noise model. It does not
provide the classification accuracy of a well-trained ML system on a labeled
historical dataset. And its detection advantage over SPC is largest for slow
monotone drift --- in regimes with abrupt step changes or high-frequency
disturbances, SPC and GLR-based methods remain more powerful.

These limitations define the operating boundary. The framework is strongest
where drift is slow, structured, and below SPC alarm thresholds --- which is
precisely the regime of most costly undetected process degradation in
semiconductor manufacturing.

%% ═══════════════════════════════════════════════════════════════════════════
\section{Stage II Public-Benchmark Demonstration: SECOM}
\label{sec:demonstration}
%% ═══════════════════════════════════════════════════════════════════════════

\subsection{Dataset Description}

The SECOM dataset (UCI ML Repository, Olszewski 2001) is a recognized public
benchmark for inline sensor time-series in semiconductor wafer fabrication.
It contains:
\begin{itemize}
  \item \textbf{1,567 wafer runs} with preserved temporal order;
  \item \textbf{590 anonymized sensor measurements} per run, covering a
        range of process steps in a real fab environment;
  \item \textbf{binary pass/fail labels} ($-1$ = pass, $+1$ = fail), with
        approximately 93 failures (5.9\% failure rate);
  \item \textbf{timestamps} for each run;
  \item and significant missing data ($\sim$5--15\% missing values per
        feature), reflecting real fab data quality conditions.
\end{itemize}

The dataset does not identify the specific process steps, tools, chambers, or
fab. That anonymization is a feature for public benchmarking but also a
material limit for interpretation. SECOM supports real-data evaluation of
residual structure and failure-preceding motifs on semiconductor data, but it
does not by itself validate physical root-cause attribution, chamber-mechanism
identification, or universal early-warning superiority.

\subsection{Experimental Setup}

The demonstration applies the structural semiotics engine to a selected subset
of SECOM sensor channels exhibiting interpretable drift structure. The
methodology uses the following fixed Stage~II protocol:

\begin{enumerate}
  \item \textbf{Nominal reference:} the mean sensor value over the first
        100 passing wafer runs (healthy window) is used as the nominal
        prediction $\hat{x}$.
  \item \textbf{Residual construction:} $r(k) = x(k) - \hat{x}$ for each
        run $k$ and each selected sensor channel.
  \item \textbf{Envelope parameterization:} the admissibility envelope radius
        $\rho$ is set at $3\sigma$ of the residual distribution over the
        healthy window, derived from data without hand-tuning.
  \item \textbf{Drift detection:} finite-difference drift $\dot{r}(k)$ is
        computed over a window of $W = 5$ consecutive runs.
  \item \textbf{Structural alarm:} fires when mean drift $\geq \alpha$ and
        residual norm $> 0.5\rho$ (boundary-entry condition).
  \item \textbf{Baseline:} a $3\sigma$ magnitude threshold, alarming when
        $|r(k)| > \rho$.
\end{enumerate}

\subsection{Baseline Scope and Comparator Discipline}

The current empirical comparator is intentionally narrow: a univariate
$3\sigma$ magnitude threshold. This is a weak baseline, not a complete
industrial comparison set. It is appropriate for demonstrating the difference
between scalar alarms and typed residual interpretation, but it should not be
read as a head-to-head comparison against the stronger comparators used in
serious semiconductor FDC studies. Later stages should compare against EWMA and
CUSUM drift detectors, PCA/Hotelling $T^2$/SPE-style multivariate FDC
baselines, and lightweight ML anomaly baselines where labels and deployment
context justify them.

\subsection{Reproducibility and Artifact Discipline}

This version is reproducible at the protocol level rather than as a packaged
crate artifact. The manuscript fixes the dataset source, healthy window, nominal
reference, residual construction, $3\sigma$ envelope, drift window ($W=5$),
boundary-entry rule, and threshold comparator. At the time of writing, no
repo-local benchmark script, Colab notebook, or versioned SECOM result file is
present under \texttt{crates/dsfb-semiconductor/paper}; adding runnable crate
artifacts is a Stage~III task rather than a claim of the present paper.

\subsection{Results and Interpretation}

\begin{tcolorbox}[warnbox]
\textbf{Scope note.} The SECOM dataset provides pass/fail labels per wafer run
but does not provide continuous degradation ground truth. Because the current
comparator is also only a $3\sigma$ magnitude threshold, this section should be
read as Stage~II interpretive feasibility rather than a definitive industrial
benchmark.
\end{tcolorbox}

The manuscript-level result is qualitative and bounded. On real semiconductor
data, the structural layer can emit typed trajectory states such as
\texttt{SustainedOutwardDrift}, \texttt{RecurrentBoundaryGrazing}, and
\texttt{AbruptSlewViolation} under a fixed protocol, whereas the threshold
baseline remains magnitude-only. This supports the claim that structured
residual interpretation is feasible on public semiconductor data. It does not
establish universal performance superiority, fab readiness, or complete
fault-coverage validation.

The interpretive output is the operationally valuable result. A process engineer
receiving a \texttt{SustainedOutwardDrift} alarm on a specific sensor channel
has more specific information than a scalar threshold crossing alone: the
process appears to be moving steadily toward inadmissibility rather than merely
exhibiting a single large excursion. That distinction can support a maintenance
review or tighter watch, but the correct intervention still depends on the tool,
recipe, and fab action policy.

\subsection{Heuristics Bank Population}

The current Stage~II evidence justifies only a small, provenance-aware seed
bank. The table below records what is observed in SECOM and what remains
interpretive hypothesis.

\begin{center}
\small
\renewcommand{\arraystretch}{1.25}
\begin{tabularx}{\linewidth}{@{}p{2.5cm}p{3.1cm}p{2.6cm}X p{2.4cm}@{}}
\toprule
\textbf{Motif class} & \textbf{Residual signature} & \textbf{Grammar state} &
\textbf{Operational interpretation} & \textbf{Provenance status} \\
\midrule
Pre-failure slow drift &
Persistent positive drift over tens to hundreds of runs before a failure label &
\texttt{SustainedOutwardDrift} &
Candidate early-warning drift motif; supports tighter monitoring or maintenance
review rather than immediate mechanism attribution &
SECOM-observed \\

Transient excursion &
Brief slew spike followed by return toward admissible range &
\texttt{AbruptSlewViolation} $\rightarrow$ \texttt{Admissible} &
Compatible with transient upset or recipe-step change, but not uniquely
identified &
SECOM-observed; interpretation hypothesis \\

Recurrent boundary approach &
Repeated near-boundary excursions without a clean sustained exit &
\texttt{RecurrentBoundaryGrazing} &
Ambiguous precursor motif that warrants continued observation rather than a
definitive diagnosis &
SECOM-observed \\
\bottomrule
\end{tabularx}
\end{center}

These entries seed a reusable heuristics bank, but they are intentionally
bounded. The provenance field is part of the argument: the table does not claim
that SECOM alone yields verified physical failure mechanisms.

\subsection{Primary Real-World Dataset Path}

The next primary benchmark target for the Rust crate and planned Colab notebook
is the PHM 2018 ion mill etch tool dataset. This is a benchmark-selection
roadmap statement, not a report of results. The motivation is methodological:
a benchmark organized around degradation progression is a better fit for
early-warning and run-to-failure evaluation than SECOM's anonymized pass/fail
framing. SECOM remains useful as a secondary public benchmark because it
exposes the method to real semiconductor sensor data, missingness, and
failure-preceding residual motifs under anonymization.

%% ═══════════════════════════════════════════════════════════════════════════
\section{Qualification Relevance and Integration Pathway}
\label{sec:certification}
%% ═══════════════════════════════════════════════════════════════════════════

\subsection{Why SEMI E10 and E116 Matter Here}

SEMI~E10 defines equipment reliability, availability, and maintainability
metrics for semiconductor manufacturing equipment. SEMI~E116 addresses
equipment performance tracking and is relevant when fabs discuss monitoring
discipline, traceability, and reproducible evaluation. In this paper those
standards are cited only to explain why determinism, explicit alarm logic, and
traceable intermediate states matter. The paper does \emph{not} claim that the
theorems presented here themselves establish compliance with either standard.

\subsection{What the DSFB Layer Contributes}

As an augmentation layer on top of existing SPC/APC/FDC residual streams, DSFB
contributes three properties that are relevant to later qualification work:

\begin{enumerate}
  \item \textbf{Deterministic interpretation under fixed inputs and
        parameters,} which supports reproducible review.
  \item \textbf{Explicit intermediate representations} --- residual, drift,
        slew, grammar state, semantic disposition --- that can be documented
        and audited by process engineers.
  \item \textbf{Control-loop separation,} because the layer reads residuals
        without rewriting the incumbent APC controller.
\end{enumerate}

These properties support an auditability argument and a plausible integration
pathway. They are relevant to qualification workflows, but they are not a
substitute for deployment-specific qualification evidence.

\subsection{What Remains Deployment-Dependent}

Formal qualification remains future work and is necessarily deployment-context
dependent. Tool family, recipe, alarm governance, missing-data policy, envelope
calibration, human response procedures, and acceptance-test criteria all affect
what would need to be demonstrated in a real fab. The correct near-term claim is
therefore modest: DSFB provides deterministic and reproducible intermediate
representations that position the method for later qualification work; it is
not itself a completed qualification report.

%% ═══════════════════════════════════════════════════════════════════════════
\section{Limitations}
\label{sec:limitations}
%% ═══════════════════════════════════════════════════════════════════════════

\subsection{Dependence on Nominal Model Quality}

The residual is defined relative to a nominal predictor. In semiconductor
process control, the nominal predictor is typically an EWMA-smoothed
historical mean or a first-principles process model. If the nominal model
is poorly specified --- if it does not capture systematic process drifts that
are part of normal operation, or if the healthy window used to estimate the
mean is contaminated by early degradation events --- then the residual
organization may reflect modeling artifact rather than process-internal
structure.

\subsection{Envelope Calibration Across Tool Families}

Admissibility envelopes derived from one tool's qualification window may not
transfer directly to a second tool of the same type due to chamber-to-chamber
variation, tool history differences, and process recipe differences. The
framework does not yet provide a universal envelope transfer methodology.
Envelope calibration remains a per-tool, per-process engineering activity.

\subsection{Failure Modes and Non-Ideal Operating Regimes}

Several operating regimes are difficult for a structural residual interpreter
and should be treated as explicit failure modes rather than edge cases:
\begin{itemize}
  \item \textbf{Abrupt but weakly structured faults:} a sudden excursion with
        little precursor organization may still be handled better by threshold,
        GLR, or fast multivariate detectors than by grammar-based drift logic.
  \item \textbf{Poor nominal-reference definition:} if the healthy window or
        nominal predictor is contaminated, the resulting residual may encode
        modeling error rather than process degradation.
  \item \textbf{Recipe-driven regime shifts:} intentional set-point changes,
        chamber cleans, or product transitions can mimic structural drift unless
        the regime context is represented explicitly.
  \item \textbf{Heavy missingness:} repeated imputation or sparse channels can
        distort drift and slew estimates and make grammar-state assignment
        ambiguous.
  \item \textbf{Cross-tool envelope miscalibration:} envelopes set on one tool,
        chamber, or maintenance state may over-alarm or under-alarm on another.
  \item \textbf{Anonymized channels:} when public datasets hide tool and sensor
        identity, the semiotic trajectory may still be legible while the
        operational interpretation remains weakly grounded.
\end{itemize}

In these regimes the correct role for DSFB is as an adjunct interpretive layer,
not as decisive evidence by itself.

\subsection{SECOM Empirical Scope}

The SECOM dataset provides pass/fail labels but not continuous degradation
ground truth. The Stage~II demonstration establishes only that the engine can
produce interpretable semiotic trajectories on real fab data under a fixed
protocol. It does not provide chamber-level root-cause attribution, a
head-to-head latency comparison against stronger industrial baselines, or
evidence for universal early-warning advantage. Those are later-stage
evaluation tasks.

\subsection{Missing Data Handling}

The SECOM dataset contains significant missing values. The demonstration
applies mean imputation over the healthy window, which is a conservative
strategy. More sophisticated imputation methods, or channel selection to
exclude high-missingness features, may affect detection results. A
systematic missing data strategy for the semiconductor application is
deferred to a future paper.

\subsection{Deployment Scope and Qualification Boundary}

This paper is not a deployment paper. It does not establish automated recipe
changes, fab-specific human response policies, fleet-level chamber ranking, or
completed qualification. The framework processes one residual trajectory at a
time. Fleet-level monitoring and chamber-to-chamber coordination require the
hierarchical extensions of the general framework together with tool-specific
qualification evidence that is not yet provided here.

%% ═══════════════════════════════════════════════════════════════════════════
\section{Conclusion}
\label{sec:conclusion}
%% ═══════════════════════════════════════════════════════════════════════════

\subsection{Main Contribution}

This paper has presented the application of the DSFB Structural Semiotics
Engine to semiconductor process control. The central contribution is a formal
augmentation architecture in which the structural semiotics engine reads the
innovation residuals produced by existing SPC, EWMA, and FDC infrastructure
and provides a typed, deterministic, auditable structural interpretation
alongside the scalar alarm outputs those systems already produce.

The framework does not replace incumbent probabilistic methods. Its value lies
in adding a deterministic interpretive layer on top of existing residual
streams, so that process engineers can review drift direction, boundary
approach, and provenance-aware motif matches instead of only receiving scalar
alarm magnitudes.

\subsection{What This Paper Establishes}

The paper establishes the following at the level of general methodology:

\begin{itemize}
  \item A formal mapping of DSFB objects onto semiconductor process control
        constructs, showing that the framework's formal results apply directly
        to R2R innovation residuals, SPC control limits, and EWMA controllers.
  \item An augmentation architecture with a clean residual handoff that
        modifies nothing in the existing control loop.
  \item A bounded decision-support logic in which DSFB states can be reviewed
        alongside incumbent scalar alarms.
  \item A Stage~II demonstration on the SECOM public dataset establishing
        interpretive feasibility on real semiconductor data under a fixed
        protocol and a weak threshold baseline.
  \item A qualification-relevance argument based on deterministic intermediate
        representations, without claiming completed standards compliance or fab
        qualification.
\end{itemize}

\subsection{What Has Not Been Claimed}

This paper has not claimed universal superiority over SPC, FDC, or ML-based
fault detection. It has not claimed that the SECOM demonstration constitutes
complete empirical validation for all semiconductor process classes. It has
not claimed that envelope calibration is automatic or transferable without
engineering judgment. And it has not claimed that the current heuristics bank
is mature enough to replace process engineering expertise. It has also not
claimed SEMI compliance, completed qualification, or physical root-cause
attribution from anonymized SECOM channels.

\subsection{Future Work}

Stage~III should add runnable crate and notebook artifacts, wire the Rust
online engine to benchmark data streams, and compare against stronger baseline
families including EWMA/CUSUM drift detectors, PCA/Hotelling $T^2$/SPE
multivariate FDC baselines, and lightweight ML anomaly detectors where
appropriate. The next primary benchmark target for that stage is the PHM 2018
ion mill etch tool dataset, which is a better fit for early-warning and
run-to-failure evaluation than SECOM's anonymized pass/fail framing. Fleet-level
coordinated monitoring and deployment-specific qualification remain subsequent
milestones.

\subsection{Closing Statement}

The structural semiotics engine proposes a precise and bounded claim for
semiconductor process control: the innovation residuals that existing
controllers already produce contain structured temporal information that
scalar methods discard, and that information can be recovered and formalized as
a deterministic interpretive layer without replacing existing infrastructure.
The value of that claim lies not in universal superiority, but in bounded
operator legibility: a reusable, auditable intermediate representation that can
support later qualification work and more disciplined benchmarking on richer
semiconductor datasets.

%% ─── References ──────────────────────────────────────────────────────────────
\begin{thebibliography}{99}

\bibitem{dsfb-semiotics-general}
De Beer, R. (2026).
\textit{DSFB Structural Semiotics Engine for General Systems:
A Deterministic Endoduction Framework for Residual-Based Meaning Extraction}
(v1.0). Zenodo. \url{https://doi.org/10.5281/zenodo.19176473}

\bibitem{secom}
Olszewski, R.T. (2001).
\textit{Generalized Feature Extraction for Structural Pattern Recognition
in Time-Series Data}. PhD Thesis, Carnegie Mellon University.
UCI ML Repository SECOM Dataset, ID~179.
\url{https://archive.ics.uci.edu/dataset/179/secom}

\bibitem{frank1990}
Frank, P.M. (1990).
Fault diagnosis in dynamic systems using analytical and knowledge-based
redundancy: A survey and some new results.
\textit{Automatica}, 26(3), 459--474.

\bibitem{isermann2005}
Isermann, R. (2005).
Model-based fault-detection and diagnosis: Status and applications.
\textit{Annual Reviews in Control}, 29(1), 71--85.

\bibitem{gertler1998}
Gertler, J. (1998).
\textit{Fault Detection and Diagnosis in Engineering Systems}.
Marcel Dekker.

\bibitem{moyne2000}
Moyne, J., del Castillo, E., \& Hurwitz, A.M. (2000).
\textit{Run-to-Run Control in Semiconductor Manufacturing}.
CRC Press.

\bibitem{semi_e10}
SEMI E10 (2022).
\textit{Specification for Definition and Measurement of Equipment Reliability,
Availability, and Maintainability (RAM) and Utilization}.
SEMI International Standards.

\bibitem{semi_e116}
SEMI E116 (2020).
\textit{Specification for Equipment Performance Tracking}.
SEMI International Standards.

\bibitem{qin2003}
Qin, S.J. (2003).
Statistical process monitoring: Basics and beyond.
\textit{Journal of Chemometrics}, 17(8--9), 480--502.

\bibitem{pca_fdc}
Wise, B.M., \& Gallagher, N.B. (1996).
The process chemometrics approach to process monitoring and fault detection.
\textit{Journal of Process Control}, 6(6), 329--348.

\bibitem{ewma_r2r}
Butler, S.W., \& Stefani, J.A. (1994).
Supervisory run-to-run control of polysilicon gate etch using in situ
ellipsometry.
\textit{IEEE Transactions on Semiconductor Manufacturing}, 7(2), 193--201.

\end{thebibliography}

\end{document}
